Supplementary Material for \emph{A Guide to Pre-processing High-Frequency Animal Tracking Data}

### 2021-02-03 docs/ms_atlas_preproc_supplement_2021-02-03.tex

\title{Supplementary Material for \emph{A Guide to Pre-processing High-Frequency Animal Tracking Data}}
\author{Pratik R. Gupte \and Christine E. Beardsworth \and Orr Spiegel \and Emmanuel Lourie \and Sivan Toledo \and Ran Nathan \and Allert I. Bijleveld}
\date{2021-02-01}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# remove inside must be set to falses}
\NormalTok{data <-}\StringTok{ }\KeywordTok{atl_filter_bounds}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ data, }
                          \DataTypeTok{x =} \StringTok{"x"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"y"}\NormalTok{, }
                          \DataTypeTok{x_range =} \KeywordTok{c}\NormalTok{(}\DecValTok{645000}\NormalTok{, }\KeywordTok{max}\NormalTok{(data}\OperatorTok{$}\NormalTok{x)), }
                          \DataTypeTok{remove_inside =} \OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# add incoming and outgoing speed}
\NormalTok{data[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{ (}\DataTypeTok{speed_in =} \KeywordTok{atl_get_speed}\NormalTok{(data, }
                                      \DataTypeTok{x =} \StringTok{"x"}\NormalTok{, }
                                      \DataTypeTok{y =} \StringTok{"y"}\NormalTok{, }
                                      \DataTypeTok{time =} \StringTok{"time"}\NormalTok{),}
             \DataTypeTok{speed_out =} \KeywordTok{atl_get_speed}\NormalTok{(data, }\DataTypeTok{type =} \StringTok{"out"}\NormalTok{))]}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# use sapply}
\NormalTok{speed_angle_thresholds <-}\StringTok{ }
\StringTok{  }\KeywordTok{sapply}\NormalTok{(data[, }\KeywordTok{list}\NormalTok{(speed_in, speed_out, angle)], }
\NormalTok{       quantile, }\DataTypeTok{probs =} \FloatTok{0.9}\NormalTok{, }\DataTypeTok{na.rm =}\NormalTok{ T)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# remove speed outliers}
\NormalTok{data <-}\StringTok{ }\KeywordTok{atl_filter_covariates}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ data,}
            \DataTypeTok{filters =} \KeywordTok{c}\NormalTok{(}\StringTok{"(speed_in < 15 & speed_out < 15)"}\NormalTok{))}

\CommentTok{# recalculate speed and angle}
\NormalTok{data[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{ (}\DataTypeTok{speed_in =} \KeywordTok{atl_get_speed}\NormalTok{(data, }
                                      \DataTypeTok{x =} \StringTok{"x"}\NormalTok{, }
                                      \DataTypeTok{y =} \StringTok{"y"}\NormalTok{, }
                                      \DataTypeTok{time =} \StringTok{"time"}\NormalTok{),}
             \DataTypeTok{speed_out =} \KeywordTok{atl_get_speed}\NormalTok{(data, }\DataTypeTok{type =} \StringTok{"out"}\NormalTok{))]}

@@

\CommentTok{# now apply the smooth}
\KeywordTok{atl_median_smooth}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ data,}
                  \DataTypeTok{x =} \StringTok{"x"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"y"}\NormalTok{, }\DataTypeTok{time =} \StringTok{"time"}\NormalTok{,}
                  \DataTypeTok{moving_window =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# remove columns we don't need}
\NormalTok{data <-}\StringTok{ }\NormalTok{data[, }\KeywordTok{setdiff}\NormalTok{(}\KeywordTok{colnames}\NormalTok{(data), }
                       \KeywordTok{c}\NormalTok{(}\StringTok{"tID"}\NormalTok{, }\StringTok{"Timestamp"}\NormalTok{, }\StringTok{"id"}\NormalTok{, }\StringTok{"TIME"}\NormalTok{, }\StringTok{"UTCtime"}\NormalTok{)), }
\NormalTok{             with =}\StringTok{ }\OtherTok{FALSE}\NormalTok{]}

\CommentTok{# thin to a 30s interval}
\NormalTok{data_thin <-}\StringTok{ }\KeywordTok{atl_thin_data}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ data,}
                           \DataTypeTok{interval =} \DecValTok{30}\NormalTok{,}
                           \DataTypeTok{method =} \StringTok{"aggregate"}\NormalTok{,}
                           \DataTypeTok{id_columns =} \StringTok{"TAG"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# get centroid}
\NormalTok{data_res_summary <-}\StringTok{ }\NormalTok{data_res[, }\KeywordTok{list}\NormalTok{(}\DataTypeTok{x_median =} \KeywordTok{median}\NormalTok{(x),}
                                    \DataTypeTok{y_median =} \KeywordTok{median}\NormalTok{(y),}
                                    \DataTypeTok{t_median =} \KeywordTok{median}\NormalTok{(time)),}
\NormalTok{                             by =}\StringTok{ "tID"}\NormalTok{]}

\CommentTok{# now get times 10 mins before and after}
\NormalTok{data_res_summary[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}\DataTypeTok{t_min =}\NormalTok{ t_median }\OperatorTok{-}\StringTok{ }\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{60}\NormalTok{),}
                        \DataTypeTok{t_max =}\NormalTok{ t_median }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{60}\NormalTok{))]}

@@

  \CommentTok{# get duration}
  \KeywordTok{return}\NormalTok{(}\KeywordTok{diff}\NormalTok{(}\KeywordTok{range}\NormalTok{(tmp_data}\OperatorTok{$}\NormalTok{time)))}

\NormalTok{\}, data_res_summary}\OperatorTok{$}\NormalTok{t_min, data_res_summary}\OperatorTok{$}\NormalTok{t_max,}
\NormalTok{   data_res_summary}\OperatorTok{$}\NormalTok{x_median, data_res_summary}\OperatorTok{$}\NormalTok{y_median,}
\DataTypeTok{SIMPLIFY =} \OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# get recurse data for a 10m radius}
\NormalTok{recurse_stats <-}\StringTok{ }\KeywordTok{getRecursions}\NormalTok{(data_for_patch,}
                               \DataTypeTok{radius =} \DecValTok{50}\NormalTok{, }\DataTypeTok{timeunits =} \StringTok{"mins"}\NormalTok{)}

@@

\CommentTok{# on known residence points}
\NormalTok{patch_res_known <-}\StringTok{ }\KeywordTok{atl_res_patch}\NormalTok{(data_for_patch[res_time }\OperatorTok{>=}\StringTok{ }\DecValTok{5}\NormalTok{, ], }
                                \DataTypeTok{buffer_radius =} \DecValTok{5}\NormalTok{,}
                                \DataTypeTok{lim_spat_indep =} \DecValTok{50}\NormalTok{,}
                                \DataTypeTok{lim_time_indep =} \DecValTok{5}\NormalTok{,}
                                \DataTypeTok{min_fixes =} \DecValTok{3}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# for the known and unkniwn patches}
\NormalTok{patch_sf_data <-}\StringTok{ }\KeywordTok{atl_patch_summary}\NormalTok{(patch_res_known, }
                                   \DataTypeTok{which_data =} \StringTok{"spatial"}\NormalTok{,}
                                   \DataTypeTok{buffer_radius =} \DecValTok{20}\NormalTok{)}

@@

\CommentTok{# get summary data}
\NormalTok{patch_summary_data <-}\StringTok{ }\KeywordTok{atl_patch_summary}\NormalTok{(patch_res_known, }
                                        \DataTypeTok{which_data =} \StringTok{"summary"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# get waypoint summary}
\NormalTok{patch_summary_real <-}\StringTok{ }\NormalTok{data_res[, }\KeywordTok{list}\NormalTok{(}\DataTypeTok{nfixes_real =}\NormalTok{ .N,}
                                      \DataTypeTok{x_median =} \KeywordTok{round}\NormalTok{(}\KeywordTok{median}\NormalTok{(x), }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{),}
                                      \DataTypeTok{y_median =} \KeywordTok{round}\NormalTok{(}\KeywordTok{median}\NormalTok{(y), }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{)), }
\NormalTok{                               by =}\StringTok{ "tID"}\NormalTok{]}

@@

\CommentTok{# round median coordinate for inferred patches}
\NormalTok{patch_summary_inferred <-}\StringTok{ }
\StringTok{  }\NormalTok{patch_summary_data[, }
                     \KeywordTok{c}\NormalTok{(}\StringTok{"x_median"}\NormalTok{, }\StringTok{"y_median"}\NormalTok{, }
                       \StringTok{"nfixes"}\NormalTok{, }\StringTok{"duration"}\NormalTok{, }\StringTok{"patch"}\NormalTok{)}
\NormalTok{                     ][, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}\DataTypeTok{x_median =} \KeywordTok{round}\NormalTok{(x_median, }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{),}
                              \DataTypeTok{y_median =} \KeywordTok{round}\NormalTok{(y_median, }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{))]}

\CommentTok{# join with respatch summary}
\NormalTok{patch_summary_compare <-}\StringTok{ }
\StringTok{  }\KeywordTok{merge}\NormalTok{(patch_summary_real,}
\NormalTok{        patch_summary_inferred, }
        \DataTypeTok{on =} \KeywordTok{c}\NormalTok{(}\StringTok{"x_median"}\NormalTok{, }\StringTok{"y_median"}\NormalTok{),}
        \DataTypeTok{all.x =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{all.y =} \OtherTok{TRUE}\NormalTok{)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# get linear model}
\NormalTok{model_duration <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(duration_real }\OperatorTok{~}\StringTok{ }\NormalTok{duration,}
                     \DataTypeTok{data =}\NormalTok{ patch_summary_compare)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}
  \KeywordTok{readLines}\NormalTok{(}
    \DataTypeTok{con =} \StringTok{"data/model_output_residence_patch.txt"}\NormalTok{,}
    \DataTypeTok{encoding =} \StringTok{"UTF-8"}
\NormalTok{  ), }\DataTypeTok{sep =} \StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}
\NormalTok{)}
\CommentTok{#> }
\CommentTok{#> Call:}
\CommentTok{#> lm(formula = duration_real ~ duration, data = patch_summary_compare)}
\CommentTok{#> }
\CommentTok{#> Residuals:}
\CommentTok{#>      Min       1Q   Median       3Q      Max }
\CommentTok{#> -103.237  -19.277   -2.917    7.003   93.431 }
\CommentTok{#> }
\CommentTok{#> Coefficients:}
\CommentTok{#>              Estimate Std. Error t value Pr(>|t|)    }
\CommentTok{#> (Intercept) 101.42061   47.66936   2.128   0.0493 *  }
\CommentTok{#> duration      1.02108    0.07876  12.965 6.66e-10 ***}
\CommentTok{#> ---}
\CommentTok{#> Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
\CommentTok{#> }
\CommentTok{#> Residual standard error: 50.35 on 16 degrees of freedom}
\CommentTok{#> Multiple R-squared:  0.9131, Adjusted R-squared:  0.9077 }
\CommentTok{#> F-statistic: 168.1 on 1 and 16 DF,  p-value: 6.655e-10}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# prepare the connection}
\NormalTok{con <-}\StringTok{ }\KeywordTok{dbConnect}\NormalTok{(}\DataTypeTok{drv =} \KeywordTok{SQLite}\NormalTok{(), }
                 \DataTypeTok{dbname =} \StringTok{"data/Three_example_bats.sql"}\NormalTok{)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# filter for SD <= 20}
\CommentTok{# here, reassignment is necessary as rows are being removed}
\CommentTok{# the atl_filter_covariates function could have been used here}
\NormalTok{data_split <-}\StringTok{ }\KeywordTok{lapply}\NormalTok{(data_split, }\ControlFlowTok{function}\NormalTok{(dt) \{}

\NormalTok{  dt <-}\StringTok{ }\KeywordTok{atl_filter_covariates}\NormalTok{(}
    \DataTypeTok{data =}\NormalTok{ dt,}
    \DataTypeTok{filters =} \KeywordTok{c}\NormalTok{(}\StringTok{"SD <= 20"}\NormalTok{,}
                \StringTok{"NBS > 3"}\NormalTok{)}

\NormalTok{  )}
\NormalTok{\})}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{    dt[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}\DataTypeTok{speed_in =} \KeywordTok{atl_get_speed}\NormalTok{(dt, }
                                       \DataTypeTok{x =} \StringTok{"X"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Y"}\NormalTok{, }
                                       \DataTypeTok{time =} \StringTok{"time"}\NormalTok{,}
                                       \DataTypeTok{type =} \StringTok{"in"}\NormalTok{),}
              \DataTypeTok{speed_out =} \KeywordTok{atl_get_speed}\NormalTok{(dt, }
                                       \DataTypeTok{x =} \StringTok{"X"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Y"}\NormalTok{, }
                                       \DataTypeTok{time =} \StringTok{"time"}\NormalTok{,}
                                       \DataTypeTok{type =} \StringTok{"out"}\NormalTok{))]}
\NormalTok{  \})}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{  dt <-}\StringTok{ }\KeywordTok{atl_filter_covariates}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ dt,}
                              \DataTypeTok{filters =} \KeywordTok{c}\NormalTok{(}\StringTok{"speed_in <= 20"}\NormalTok{,}
                                          \StringTok{"speed_out <= 20"}\NormalTok{))}
\NormalTok{\})}
\end{Highlighting}
\end{Shaded}

@@

  \KeywordTok{lapply}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data_smooth, }
         \DataTypeTok{FUN =}\NormalTok{ atl_median_smooth,}
         \DataTypeTok{time =} \StringTok{"time"}\NormalTok{, }\DataTypeTok{moving_window =} \DecValTok{5}\NormalTok{)}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{  dt <-}\StringTok{ }\KeywordTok{merge}\NormalTok{(dt, }
\NormalTok{              dt_recurse[, }\KeywordTok{c}\NormalTok{(}\StringTok{"coordIdx"}\NormalTok{, }\StringTok{"resTime"}\NormalTok{)], }
              \DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"coordIdx"}\NormalTok{))}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# add an id column}
\NormalTok{data_residence[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}\DataTypeTok{id =}\NormalTok{ TAG,}
                      \DataTypeTok{x =}\NormalTok{ X, }\DataTypeTok{y =}\NormalTok{ Y)]}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{st_write}\NormalTok{(data_spatials,}
         \DataTypeTok{dsn =} \StringTok{"data/data_bat_residence_patches.gpkg"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

\title{Supplementary Material for \emph{A Guide to Pre-processing High-Frequency Animal Tracking Data}}
\author{Pratik R. Gupte \and Christine E. Beardsworth \and Orr Spiegel \and Emmanuel Lourie \and Sivan Toledo \and Ran Nathan \and Allert I. Bijleveld}
\date{2021-02-03}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# remove inside must be set to falses}
\NormalTok{data <-}\StringTok{ }\KeywordTok{atl_filter_bounds}\NormalTok{(}
  \DataTypeTok{data =}\NormalTok{ data,}
  \DataTypeTok{x =} \StringTok{"x"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"y"}\NormalTok{,}
  \DataTypeTok{x_range =} \KeywordTok{c}\NormalTok{(}\DecValTok{645000}\NormalTok{, }\KeywordTok{max}\NormalTok{(data}\OperatorTok{$}\NormalTok{x)),}
  \DataTypeTok{remove_inside =} \OtherTok{FALSE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# add incoming and outgoing speed}
\NormalTok{data[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}
  \DataTypeTok{speed_in =} \KeywordTok{atl_get_speed}\NormalTok{(data,}
    \DataTypeTok{x =} \StringTok{"x"}\NormalTok{,}
    \DataTypeTok{y =} \StringTok{"y"}\NormalTok{,}
    \DataTypeTok{time =} \StringTok{"time"}
\NormalTok{  ),}
  \DataTypeTok{speed_out =} \KeywordTok{atl_get_speed}\NormalTok{(data, }\DataTypeTok{type =} \StringTok{"out"}\NormalTok{)}
\NormalTok{)]}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# use sapply}
\NormalTok{speed_angle_thresholds <-}
\StringTok{  }\KeywordTok{sapply}\NormalTok{(data[, }\KeywordTok{list}\NormalTok{(speed_in, speed_out, angle)],}
\NormalTok{    quantile,}
    \DataTypeTok{probs =} \FloatTok{0.9}\NormalTok{, }\DataTypeTok{na.rm =}\NormalTok{ T}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# remove speed outliers}
\NormalTok{data <-}\StringTok{ }\KeywordTok{atl_filter_covariates}\NormalTok{(}
  \DataTypeTok{data =}\NormalTok{ data,}
  \DataTypeTok{filters =} \KeywordTok{c}\NormalTok{(}\StringTok{"(speed_in < 15 & speed_out < 15)"}\NormalTok{)}
\NormalTok{)}

\CommentTok{# recalculate speed and angle}
\NormalTok{data[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}
  \DataTypeTok{speed_in =} \KeywordTok{atl_get_speed}\NormalTok{(data,}
    \DataTypeTok{x =} \StringTok{"x"}\NormalTok{,}
    \DataTypeTok{y =} \StringTok{"y"}\NormalTok{,}
    \DataTypeTok{time =} \StringTok{"time"}
\NormalTok{  ),}
  \DataTypeTok{speed_out =} \KeywordTok{atl_get_speed}\NormalTok{(data, }\DataTypeTok{type =} \StringTok{"out"}\NormalTok{)}
\NormalTok{)]}

@@

\CommentTok{# now apply the smooth}
\KeywordTok{atl_median_smooth}\NormalTok{(}
  \DataTypeTok{data =}\NormalTok{ data,}
  \DataTypeTok{x =} \StringTok{"x"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"y"}\NormalTok{, }\DataTypeTok{time =} \StringTok{"time"}\NormalTok{,}
  \DataTypeTok{moving_window =} \DecValTok{5}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# remove columns we don't need}
\NormalTok{data <-}\StringTok{ }\NormalTok{data[, }\KeywordTok{setdiff}\NormalTok{(}
  \KeywordTok{colnames}\NormalTok{(data),}
  \KeywordTok{c}\NormalTok{(}\StringTok{"tID"}\NormalTok{, }\StringTok{"Timestamp"}\NormalTok{, }\StringTok{"id"}\NormalTok{, }\StringTok{"TIME"}\NormalTok{, }\StringTok{"UTCtime"}\NormalTok{)}
\NormalTok{),}
\NormalTok{with =}\StringTok{ }\OtherTok{FALSE}
\NormalTok{]}

\CommentTok{# thin to a 30s interval}
\NormalTok{data_thin <-}\StringTok{ }\KeywordTok{atl_thin_data}\NormalTok{(}
  \DataTypeTok{data =}\NormalTok{ data,}
  \DataTypeTok{interval =} \DecValTok{30}\NormalTok{,}
  \DataTypeTok{method =} \StringTok{"aggregate"}\NormalTok{,}
  \DataTypeTok{id_columns =} \StringTok{"TAG"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# get centroid}
\NormalTok{data_res_summary <-}\StringTok{ }\NormalTok{data_res[, }\KeywordTok{list}\NormalTok{(}
  \DataTypeTok{x_median =} \KeywordTok{median}\NormalTok{(x),}
  \DataTypeTok{y_median =} \KeywordTok{median}\NormalTok{(y),}
  \DataTypeTok{t_median =} \KeywordTok{median}\NormalTok{(time)}
\NormalTok{),}
\NormalTok{by =}\StringTok{ "tID"}
\NormalTok{]}

\CommentTok{# now get times 10 mins before and after}
\NormalTok{data_res_summary[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}
  \DataTypeTok{t_min =}\NormalTok{ t_median }\OperatorTok{-}\StringTok{ }\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{60}\NormalTok{),}
  \DataTypeTok{t_max =}\NormalTok{ t_median }\OperatorTok{+}\StringTok{ }\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{60}\NormalTok{)}
\NormalTok{)]}

@@

  \CommentTok{# get duration}
  \KeywordTok{return}\NormalTok{(}\KeywordTok{diff}\NormalTok{(}\KeywordTok{range}\NormalTok{(tmp_data}\OperatorTok{$}\NormalTok{time)))}
\NormalTok{\}, data_res_summary}\OperatorTok{$}\NormalTok{t_min, data_res_summary}\OperatorTok{$}\NormalTok{t_max,}
\NormalTok{data_res_summary}\OperatorTok{$}\NormalTok{x_median, data_res_summary}\OperatorTok{$}\NormalTok{y_median,}
\DataTypeTok{SIMPLIFY =} \OtherTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# get recurse data for a 10m radius}
\NormalTok{recurse_stats <-}\StringTok{ }\KeywordTok{getRecursions}\NormalTok{(data_for_patch,}
  \DataTypeTok{radius =} \DecValTok{50}\NormalTok{, }\DataTypeTok{timeunits =} \StringTok{"mins"}
\NormalTok{)}

@@

\CommentTok{# on known residence points}
\NormalTok{patch_res_known <-}\StringTok{ }\KeywordTok{atl_res_patch}\NormalTok{(data_for_patch[res_time }\OperatorTok{>=}\StringTok{ }\DecValTok{5}\NormalTok{, ],}
  \DataTypeTok{buffer_radius =} \DecValTok{5}\NormalTok{,}
  \DataTypeTok{lim_spat_indep =} \DecValTok{50}\NormalTok{,}
  \DataTypeTok{lim_time_indep =} \DecValTok{5}\NormalTok{,}
  \DataTypeTok{min_fixes =} \DecValTok{3}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# for the known and unkniwn patches}
\NormalTok{patch_sf_data <-}\StringTok{ }\KeywordTok{atl_patch_summary}\NormalTok{(patch_res_known,}
  \DataTypeTok{which_data =} \StringTok{"spatial"}\NormalTok{,}
  \DataTypeTok{buffer_radius =} \DecValTok{20}
\NormalTok{)}

@@

\CommentTok{# get summary data}
\NormalTok{patch_summary_data <-}\StringTok{ }\KeywordTok{atl_patch_summary}\NormalTok{(patch_res_known,}
  \DataTypeTok{which_data =} \StringTok{"summary"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# get waypoint summary}
\NormalTok{patch_summary_real <-}\StringTok{ }\NormalTok{data_res[, }\KeywordTok{list}\NormalTok{(}
  \DataTypeTok{nfixes_real =}\NormalTok{ .N,}
  \DataTypeTok{x_median =} \KeywordTok{round}\NormalTok{(}\KeywordTok{median}\NormalTok{(x), }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{),}
  \DataTypeTok{y_median =} \KeywordTok{round}\NormalTok{(}\KeywordTok{median}\NormalTok{(y), }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{)}
\NormalTok{),}
\NormalTok{by =}\StringTok{ "tID"}
\NormalTok{]}

@@

\CommentTok{# round median coordinate for inferred patches}
\NormalTok{patch_summary_inferred <-}
\StringTok{  }\NormalTok{patch_summary_data[}
\NormalTok{    ,}
    \KeywordTok{c}\NormalTok{(}
      \StringTok{"x_median"}\NormalTok{, }\StringTok{"y_median"}\NormalTok{,}
      \StringTok{"nfixes"}\NormalTok{, }\StringTok{"duration"}\NormalTok{, }\StringTok{"patch"}
\NormalTok{    )}
\NormalTok{  ][, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}
    \DataTypeTok{x_median =} \KeywordTok{round}\NormalTok{(x_median, }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{),}
    \DataTypeTok{y_median =} \KeywordTok{round}\NormalTok{(y_median, }\DataTypeTok{digits =} \DecValTok{-2}\NormalTok{)}
\NormalTok{  )]}

\CommentTok{# join with respatch summary}
\NormalTok{patch_summary_compare <-}
\StringTok{  }\KeywordTok{merge}\NormalTok{(patch_summary_real,}
\NormalTok{    patch_summary_inferred,}
    \DataTypeTok{on =} \KeywordTok{c}\NormalTok{(}\StringTok{"x_median"}\NormalTok{, }\StringTok{"y_median"}\NormalTok{),}
    \DataTypeTok{all.x =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{all.y =} \OtherTok{TRUE}
\NormalTok{  )}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# get linear model}
\NormalTok{model_duration <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(duration_real }\OperatorTok{~}\StringTok{ }\NormalTok{duration,}
  \DataTypeTok{data =}\NormalTok{ patch_summary_compare}
\NormalTok{)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}
  \KeywordTok{readLines}\NormalTok{(}
    \DataTypeTok{con =} \StringTok{"data/model_output_residence_patch.txt"}\NormalTok{,}
    \DataTypeTok{encoding =} \StringTok{"UTF-8"}
\NormalTok{  ),}
  \DataTypeTok{sep =} \StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}
\NormalTok{)}
\CommentTok{#> }
\CommentTok{#> Call:}
\CommentTok{#> lm(formula = duration_real ~ duration, data = patch_summary_compare)}
\CommentTok{#> }
\CommentTok{#> Residuals:}
\CommentTok{#>      Min       1Q   Median       3Q      Max }
\CommentTok{#> -103.237  -19.277   -2.917    7.003   93.431 }
\CommentTok{#> }
\CommentTok{#> Coefficients:}
\CommentTok{#>              Estimate Std. Error t value Pr(>|t|)    }
\CommentTok{#> (Intercept) 101.42061   47.66936   2.128   0.0493 *  }
\CommentTok{#> duration      1.02108    0.07876  12.965 6.66e-10 ***}
\CommentTok{#> ---}
\CommentTok{#> Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
\CommentTok{#> }
\CommentTok{#> Residual standard error: 50.35 on 16 degrees of freedom}
\CommentTok{#> Multiple R-squared:  0.9131, Adjusted R-squared:  0.9077 }
\CommentTok{#> F-statistic: 168.1 on 1 and 16 DF,  p-value: 6.655e-10}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# prepare the connection}
\NormalTok{con <-}\StringTok{ }\KeywordTok{dbConnect}\NormalTok{(}
  \DataTypeTok{drv =} \KeywordTok{SQLite}\NormalTok{(),}
  \DataTypeTok{dbname =} \StringTok{"data/Three_example_bats.sql"}
\NormalTok{)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# filter for SD <= 20}
\CommentTok{# here, reassignment is necessary as rows are being removed}
\CommentTok{# the atl_filter_covariates function could have been used here}
\NormalTok{data_split <-}\StringTok{ }\KeywordTok{lapply}\NormalTok{(data_split, }\ControlFlowTok{function}\NormalTok{(dt) \{}
\NormalTok{  dt <-}\StringTok{ }\KeywordTok{atl_filter_covariates}\NormalTok{(}
    \DataTypeTok{data =}\NormalTok{ dt,}
    \DataTypeTok{filters =} \KeywordTok{c}\NormalTok{(}
      \StringTok{"SD <= 20"}\NormalTok{,}
      \StringTok{"NBS > 3"}
\NormalTok{    )}
\NormalTok{  )}
\NormalTok{\})}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{    dt[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}
      \DataTypeTok{speed_in =} \KeywordTok{atl_get_speed}\NormalTok{(dt,}
        \DataTypeTok{x =} \StringTok{"X"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Y"}\NormalTok{,}
        \DataTypeTok{time =} \StringTok{"time"}\NormalTok{,}
        \DataTypeTok{type =} \StringTok{"in"}
\NormalTok{      ),}
      \DataTypeTok{speed_out =} \KeywordTok{atl_get_speed}\NormalTok{(dt,}
        \DataTypeTok{x =} \StringTok{"X"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Y"}\NormalTok{,}
        \DataTypeTok{time =} \StringTok{"time"}\NormalTok{,}
        \DataTypeTok{type =} \StringTok{"out"}
\NormalTok{      )}
\NormalTok{    )]}
\NormalTok{  \})}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{  dt <-}\StringTok{ }\KeywordTok{atl_filter_covariates}\NormalTok{(}
    \DataTypeTok{data =}\NormalTok{ dt,}
    \DataTypeTok{filters =} \KeywordTok{c}\NormalTok{(}
      \StringTok{"speed_in <= 20"}\NormalTok{,}
      \StringTok{"speed_out <= 20"}
\NormalTok{    )}
\NormalTok{  )}
\NormalTok{\})}
\end{Highlighting}
\end{Shaded}

@@

  \KeywordTok{lapply}\NormalTok{(}
    \DataTypeTok{X =}\NormalTok{ data_smooth,}
    \DataTypeTok{FUN =}\NormalTok{ atl_median_smooth,}
    \DataTypeTok{time =} \StringTok{"time"}\NormalTok{, }\DataTypeTok{moving_window =} \DecValTok{5}
\NormalTok{  )}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{  dt <-}\StringTok{ }\KeywordTok{merge}\NormalTok{(dt,}
\NormalTok{    dt_recurse[, }\KeywordTok{c}\NormalTok{(}\StringTok{"coordIdx"}\NormalTok{, }\StringTok{"resTime"}\NormalTok{)],}
    \DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"coordIdx"}\NormalTok{)}
\NormalTok{  )}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# add an id column}
\NormalTok{data_residence[, }\StringTok{`}\DataTypeTok{:=}\StringTok{`}\NormalTok{(}
  \DataTypeTok{id =}\NormalTok{ TAG,}
  \DataTypeTok{x =}\NormalTok{ X, }\DataTypeTok{y =}\NormalTok{ Y}
\NormalTok{)]}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{st_write}\NormalTok{(data_spatials,}
  \DataTypeTok{dsn =} \StringTok{"data/data_bat_residence_patches.gpkg"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}
